\documentclass[12pt]{scrartcl}

\usepackage[printwatermark,disablegeometry]{xwatermark}

\usepackage{epsfig,amssymb}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}

\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage{hyperref}
\hypersetup{
  letterpaper,
  colorlinks,
  linkcolor=red,
  citecolor=darkgreen,
  menucolor=darkred,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={CSCE 156/156H Syllabus},
}

\usepackage{fullpage}
\usepackage{tikz}
\pagestyle{empty} %
\usepackage{subfigure}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\definecolor{MyDarkRed}{rgb}{0.45,0.08,0}
\definecolor{MyDarkGreen}{rgb}{0.08,0.45,0.08}

\definecolor{mintedBackground}{rgb}{0.95,0.95,0.95}
\definecolor{mintedInlineBackground}{rgb}{.90,.90,1}

\usepackage[newfloat=true]{minted}

\setminted{mathescape,
           linenos,
           autogobble,
           frame=none,
           framesep=2mm,
           framerule=0.4pt,
           %label=foo,
           xleftmargin=2em,
           xrightmargin=0em,
           %startinline=true,  %PHP only, allow it to omit the PHP Tags *** with this option, variables using dollar sign in comments are treated as latex math
           numbersep=10pt, %gap between line numbers and start of line
           style=default} %syntax highlighting style, default is "default"

\setmintedinline{bgcolor={mintedBackground}}
%doesn't work with the above workaround:
\setminted{bgcolor={mintedBackground}}
\setminted[text]{bgcolor={mintedBackground},linenos=false,autogobble,xleftmargin=1em}
%\setminted[php]{bgcolor=mintedBackgroundPHP} %startinline=True}
\SetupFloatingEnvironment{listing}{name=Code Sample}
\SetupFloatingEnvironment{listing}{listname=List of Code Samples}

\setlength{\parindent}{0pt} %
\setlength{\parskip}{.25cm}
\newcommand{\comment}[1]{}

\usepackage{amsmath}
\usepackage{algorithm2e}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
%NOTE: you can embed algorithms in solutions, but they cannot be floating objects; use [H] to make them non-floats

\usepackage{lastpage}

%\usepackage{titling}
\usepackage{fancyhdr}
\renewcommand*{\titlepagestyle}{fancy}
\pagestyle{fancy}
%\renewcommand*{\titlepagestyle}{fancy}
%\fancyhf{}
%\rhead{Computer Science I}
%\lhead{Guides and tutorials}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.4pt}

\lhead{~}
\chead{~}
\rhead{~}
\lfoot{\Title\ -- Syllabus}
\cfoot{~}
\rfoot{\thepage\ / \pageref*{LastPage}}

\makeatletter
\title{Computer Science II}\let\Title\@title
\subtitle{Syllabus\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-1cm}
%\author{Dr.\ Chris Bourke}
\date{Spring 2019}
\makeatother

\begin{document}

\maketitle

%\newwatermark[allpages=true,scale=5,textmark=Draft\\Draft\\Draft]{},

\hrule

\begin{quote}
``Smart data structures and dumb code works a lot better than the other way around.'' 

\hfill ---Eric S.\ Raymond, \emph{The Cathedral and the Bazaar}
\end{quote}

\section{Course Info}

\textbf{Prerequisites}: CSCE 155 and MATH 106 or equivalent

\textbf{Description}: Data structures, including linked lists, stacks, 
queues, and trees; algorithms, including searching, sorting, and 
recursion; programming language topics, including object-oriented 
programming; pointers, references, and memory management; design and 
implementation of a multilayer application with SQL database.

\textbf{Credit Hours}: 4

\textbf{Postrequisites}: This course is a prerequisite for CSCE 310
(Data Structures \& Algorithms).  A grade of C or better is required 
to move on to CSCE 310.

For all other information, see the course website.

\section{Skills Objectives}

Throughout the duration of this course, you will be presented 
with a lot of information, some of which will have immediate 
application and some whose importance is not immediately apparent.  
As a different measure of your success in this course, by the end, 
you should have the following skills.

\begin{itemize}
  \item Be able to more easily pick up and learn a new programming 
  language on your own
  \item Be able to recognize, use, design and appreciate programs 
  with an Object Oriented flavor
  \item Be able to design a database-backed application from scratch 
  given a general problem statement
  \item Be able to understand and implement basic data structures 
  as well as recognize how and when to leverage appropriate simple 
  data structures
  \item Be able to identify and analyze basic algorithms
\end{itemize}

Overall, CS2 is a continuation of CS1.  At the end of a typical CS1 
course, you should be able to approach a reasonably complex problem, 
design a top-down solution, and code a program in a high-level 
programming language.  By the end of this course your approach to 
problem solving should be modified to ask and answer design questions 
first: 

\begin{itemize} 
  \item What entities/objects would be appropriate to model this problem?
  \item How would these objects interact to solve the problem?
  \item What data structures would be the most appropriate or efficient to use? 
\end{itemize}

\section{Tentative Topics}

\begin{itemize}
  \item Introduction to Java / PHP (Honors section)
  \item Object Oriented Programming, OOP in Java
  \item Database Design, SQL, Database Connectivity (JDBC), multi-tier design
  \item Lists (array-based, linked; circular doubly-linked), Stacks \& Queues
  \item Algorithm Analysis, Recursion, Searching \& Sorting
  \item Trees; Binary Search Trees
\end{itemize}

\section{Schedule}

See the course website.

\section{Accommodations for Students with Disabilities}

It is the policy of the University of Nebraska-Lincoln to 
provide flexible and individualized accommodations to students 
with documented disabilities that may affect their ability to 
fully participate in course activities or to meet course 
requirements.  To receive accommodation services, students 
must be registered with the Services for Students with 
Disabilities (SSD) office, 232 Canfield Administration, 
472-3787 voice or TTY.

\section{Grading}

Grading will be based on labs (15 points each), assignments (points
for each will vary), and exams with the following point distributions.

\begin{table}[h]
\centering
\begin{tabular}{lrrr}
Category & Number & Points & Percent \\
\hline\hline
Labs        & 15 & 225 & 15\% \\
Assignments & 9  & 1125 & 75\% \\
Midterm     & 1  & 75 & 5\% \\
Final       & 1  & 75 & 5\% \\
\hline
Total & ~ & 1500 & 100\% 
\end{tabular}
\end{table}

\subsection{Scale}

Final letter grades will be awarded based on the following 
standard scale. This scale may be adjusted upwards if the 
instructor deems it necessary based on the final grades only.  
No scale will be made for individual assignments or exams.

\begin{table}[h]
\centering
\begin{tabular}{p{1cm}c}
Letter Grade & Percent \\
\hline\hline
A+ & $\geq 97$ \\
A  & $\geq 93$ \\
A- & $\geq 90$ \\
B+ & $\geq 87$ \\
B  & $\geq 83$ \\
B- & $\geq 80$ \\
C+ & $\geq 77$ \\
C  & $\geq 73$ \\
C- & $\geq 70$ \\
D+ & $\geq 67$ \\
D  & $\geq 63$ \\
D- & $\geq 60$ \\
F  & $<60$ \\
\end{tabular}
\end{table}

\subsection{Labs}

There are weekly labs that give you hands-on exercises for 
topics recently covered in lecture.  The purpose of lab is not 
only to give you further working experience with lecture topics, 
but also to provide you with additional information and details 
not necessarily covered in lecture.  Each lab will have some 
programming requirements and a supplemental worksheet.  

Labs are setup as a \emph{peer programming} experience.  In each 
lab, you will be randomly paired with a partner.  One of you will 
be the \emph{driver} and the other will be the \emph{navigator}.  
The navigator will be responsible for reading the instructions 
and guiding the driver.  The driver will be in charge of the 
keyboard and will type the code.  Both driver and navigator are 
responsible for developing and working through solutions together.
Neither the navigator nor the driver is ``in charge,'' it is an 
equal partnership.  Beyond your immediate pairing, you are 
encouraged to help and interact and with other pairs in the lab.

Unless otherwise stated, you are required to finish the lab by 
the end of your regular lab meeting time.  A lab instructor must 
sign off on your lab worksheet and you must turn it in to receive 
credit.  Labs that have not been completed on time may not receive
credit. This means that you \emph{must} show up to your lab on
time and be properly prepared.  Being prepared means having gone
through the relevant material and pre-lab required reading.  It 
means not being preoccupied with material or questions not related
to the lab material.  

\subsection{Assignments}

There are 8 assignments.  Assignments will be due 1 second before 
midnight Friday evening the week that they are due.  Code and other 
relevant \emph{artifacts} must be submitted using CSE's webhandin.  
If there are written portions of the homework, they should be typed.  
You should typeset code snippets using a monotype font (Courier for 
example) for readability.  Figures may be hand drawn, but you are 
encouraged to use some sort of software to render them.  

In this course, most of the assignments build on prior assignments.  
Therefore, it is extremely important for you to stay on task and not 
fall behind with assignments.  You should start on assignments early 
and resolve any and all issues (bugs, design flaws) as soon as 
possible so they do not carry over to the next assignment.

Note: the final homework may be due as late as Friday of Dead Week.  
As per the 15th week policy, this serves as notice.

\subsection{Exams}

There will be a midterm exam and a comprehensive final exam.  These
will be open-book, open-note, open computer exams.  More details will 
be announced closer to the exam dates.

\subsection{15th Week Policy Notification}
\label{subsection:deadweek}

A per UNL's 15th Week Policy (available here: \url{https://registrar.unl.edu/academic-standards/policies/fifteenth-week-policy/}) we are required
to serve written notice that the final assignment
as well as the final lab and hack will be due during the 15th 
week or ``dead week.''

\subsection{Grading Policy}

If you have questions about grading or believe that points were 
deducted unfairly, you must first address the issue with the 
individual who graded it to see if it can be resolved.  Such 
questions should be made within a reasonable amount of time 
after the graded assignment has been returned.  No further 
consideration will be given to any assignment a week after 
it grades have been posted.  It is important to emphasize that 
the goal of grading is consistency.  A grade on any given 
assignment, even if it is low for the entire class, should 
not matter that much.  Rather, students who do comparable 
work should receive comparable grades (see the subsection 
on the scale used for this course).

\subsection{Late Work Policy}

%TODO: consider this

In general, there will be no make-up exams or late work
accepted.  Exceptions may be made in certain circumstances 
such as health or emergency, but you must make every effort 
to get prior permission.  Documentation may also be required.

Homework assignments have a strict due date/time as defined by
the CSE server's system clock.  All program files must be handed
in using CSE's webhandin as specified in individual assignment
handouts.  Programs that are even a few seconds past the due 
date/time will be considered late and you will be locked out
of handing anything in after that time.  

\subsection{Webgrader Policy}

Failure to adhere to the requirements of an assignment in such 
a manner that makes it impossible to grade your program via 
the webgrader means that a disproportionate amount of time 
would be spent evaluating your assignment.  For this reason, 
we will not grade any assignment that does not compile and 
run through the webgrader.  

\subsection{Academic Integrity}

All homework assignments, programs, and exams must represent
your own work unless otherwise stated.  No collaboration with 
fellow students, past or current, is allowed unless otherwise 
permitted on specific assignments or problems.  The Department of
Computer Science \& Engineering has an Academic Integrity Policy.  
All students enrolled in any computer science course are bound 
by this policy.  You are expected to read, understand, and follow 
this policy.  Violations will be dealt with on a case by case 
basis and may result in a failing assignment or a failing grade 
for the course itself.  The most recent version of the Academic 
Integrity Policy can be found at \url{http://cse.unl.edu/academic-integrity}

\subsection{Honors Section}

For those in the Honors section of this course topics will be 
covered at a faster pace so that additional ``advanced'' topics
can also be covered.  

In addition, each assignment may contain additional requirements or 
problems that must be completed.  There may also be additional 
assignments.  Bottom line, there will be higher expectations with 
regard to the quality and quantity of work in this course compared 
to the regular section.  As a student in this course, you will be 
expected to meet or exceed those expectations which may require more 
of your time and a more proactive approach to studying and greater 
diligence in completely assignments.  

\section{Communication \& Getting Help}

The primary means of communication for this course is Piazza, an online
forum system designed for college courses.  We have established a Piazza 
group for this course and you should have received an invitation to join.
If you have not, contact the instructor immediately.  With Piazza you 
can ask questions anonymously, remain anonymous to your classmates, or 
choose to be identified.  Using this open forum system the entire class 
benefits from the instructor and TA responses.  In addition, you and 
other students can also answer each other's questions (again you may
choose to remain anonymous or identify yourself to the instructors or
everyone).  You may still email the instructor or TAs, but more than 
likely you will be redirected to Piazza for help.

In addition, there are is an anonymous suggestion box that you may 
use to voice your concerns about any problems in the course if you 
do not wish to be identified. It is available at 
\url{https://cse.unl.edu/contact-form}.

\subsection{Getting Help}

Your success in this course is ultimately your responsibility.  Your
success in this course depends on how well you utilize the opportunities
and resources that we provide.  There are numerous outlets for learning
the material and getting help in this course:
\begin{itemize}
  \item Lectures: attend lectures regularly and when you do use the 
  time appropriately.  Do not distract yourself with social media or other
  time wasters.  Actively take notes (electronic or hand written).  It is
  well-documented that good note taking directly leads to understanding and
  retention of concepts.
  \item Lecture Videos: Lecture videos are intended as a supplement
  that mirrors lecture material but that may not cover everything.  Watch
  them at your own pace on a regular basis for reiteration or in case
  you missed something in lecture.  
  \item Required Reading: do the required reading on a regular basis.  The
  readings provide additional details and depth that you may not necessarily
  get directly in lecture.  
  \item Labs \& Hack Sessions: use your time during lab and hack sessions 
  wisely.  Engage with your lab instructors, teaching assistants, your partner(s)
  and other students.  Be sure to adequately prepare for labs by reading
  the handouts before coming to lab.  Get started and don't get distracted.
  \item Piazza: if you have questions ask them on Piazza.  It is the best and
  likely fastest way to get help with your questions.  Also, be sure to read
  other student's posts and questions and feel free to answer yourself!
  \item Office Hours \& Student Resource Center: the instructor and teaching
  assistants hold regular office hours throughout the week as posted on the
  course website.  Attend office hours if you have questions or want to 
  review material.  The Student Resource Center (SRC, \url{http://cse.unl.edu/src})
  Monday through Friday.  Even if your TAs are not scheduled
  during that time, there are plenty of other TAs and students present that
  may be able to help.  And, you may be able to help others!
  \item Don't procrastinate.  The biggest reason students fail this course
  is because they do not give themselves enough opportunities to learn the
  material.  Don't wait to the last minute to start your assignments.  Many
  people wait to the last minute and flood the TAs and SRC, making it difficult
  to get help as the due date approaches.  Don't underestimate how much time 
  your assignment(s) will take and don't wait to the week before hand to get 
  started.  Ideally, you should be working on the problems as we are covering 
  them.
  \item Get help in the \emph{right way}: when you go to the instructor or
  TA for help, you must demonstrate that you have put forth a good faith 
  effort toward understanding the material.  Asking questions that clearly 
  indicate you have failed to read the required material, have not been
  attending lecture, etc.\ is \emph{not acceptable}.  Don't ask generic
  questions like ``I'm lost, I don't know what I'm doing''.  Instead, 
  explain what you have tried so far.  Explain why you think what you 
  have tried doesn't seem to be working.  Then the TA will have an 
  easier time to help you identify misconceptions or problems.  This 
  is known as ``Rubber Duck Debugging'' where in if you try to explain 
  a problem to someone (or, lacking a live person, a rubber duck), 
  then you can usually identify the problem yourself.  Or, at the very 
  least, get some insight as to what might be wrong.
\end{itemize}



\end{document}
