\documentclass[12pt]{scrartcl}

\usepackage[printwatermark,disablegeometry]{xwatermark}

\usepackage{epsfig,amssymb}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}

\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage{hyperref}
\hypersetup{
  letterpaper,
  colorlinks,
  linkcolor=red,
  citecolor=darkgreen,
  menucolor=darkred,
  urlcolor=blue,
  bookmarks=true,
  pdfpagemode=none,
  pdftitle={},
  pdflang={en},
  pdfauthor={Christopher M. Bourke},
  pdfcreator={$ $Id: cv-us.tex,v 1.28 2009/01/01 00:00:00 cbourke Exp $ $},
  pdfsubject={PhD Thesis},
  pdfkeywords={}
}

\usepackage{fullpage}
\usepackage{tikz}
\pagestyle{empty} %
\usepackage{subfigure}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\definecolor{MyDarkRed}{rgb}{0.45,0.08,0}
\definecolor{MyDarkGreen}{rgb}{0.08,0.45,0.08}

\definecolor{mintedBackground}{rgb}{0.95,0.95,0.95}
\definecolor{mintedInlineBackground}{rgb}{.90,.90,1}

\usepackage[newfloat=true]{minted}

\setminted{mathescape,
           linenos,
           autogobble,
           frame=none,
           framesep=2mm,
           framerule=0.4pt,
           %label=foo,
           xleftmargin=2em,
           xrightmargin=0em,
           %startinline=true,  %PHP only, allow it to omit the PHP Tags *** with this option, variables using dollar sign in comments are treated as latex math
           numbersep=10pt, %gap between line numbers and start of line
           style=default} %syntax highlighting style, default is "default"

\setmintedinline{bgcolor={mintedBackground}}
%doesn't work with the above workaround:
\setminted{bgcolor={mintedBackground}}
\setminted[text]{bgcolor={mintedBackground},linenos=false,autogobble,xleftmargin=1em}
%\setminted[php]{bgcolor=mintedBackgroundPHP} %startinline=True}
\SetupFloatingEnvironment{listing}{name=Code Sample}
\SetupFloatingEnvironment{listing}{listname=List of Code Samples}

\setlength{\parindent}{0pt} %
\setlength{\parskip}{.25cm}
\newcommand{\comment}[1]{}

\usepackage{amsmath}
\usepackage{algorithm2e}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
%NOTE: you can embed algorithms in solutions, but they cannot be floating objects; use [H] to make them non-floats

\usepackage{lastpage}

%\usepackage{titling}
\usepackage{fancyhdr}
\renewcommand*{\titlepagestyle}{fancy}
\pagestyle{fancy}
%\renewcommand*{\titlepagestyle}{fancy}
%\fancyhf{}
%\rhead{Computer Science I}
%\lhead{Guides and tutorials}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.4pt}
\lfoot{GTA/LA Guidelines -- Computer Science I}
\cfoot{~}
\rfoot{\thepage\ / \pageref*{LastPage}}

\makeatletter
\title{Guidelines for Graduate Teaching Assistants \& Learning Assistants}\let\Title\@title
\subtitle{Computer Science II - Spring 2019\\
{\small
\vskip1cm
Department of Computer Science \& Engineering \\
University of Nebraska--Lincoln}
\vskip-1cm}
%\author{Dr.\ Chris Bourke}
\date{~}
\makeatother

\begin{document}

\maketitle

\newwatermark[allpages=true,scale=5,textmark=Draft]{},

\hrule

\section*{Overview}

The instructor sets policies in the syllabus which all students 
are expected to read, understand and adhere to. Every Graduate 
Teaching Assistant (GTA) and Learning Assistant (LA) is expected 
to read, understand and also follow these policies.  Often, 
students will attempt to violate these policies or ask for special 
consideration.  Do not speculate or otherwise discuss possible 
exceptions to these policies.  Direct them to the instructor 
and follow up with the instructor if necessary.

\begin{itemize}
  \item Be prepared.  Be aware of the course content and expectations.
  You are responsible for knowing the material so that you can effectively
  explain and demonstrate it to students.  Be able to complete the assignments, 
  labs, etc.\ yourself.  If you have doubts or concerns engage first with
  your Course Leader or GTA supervisor and/or other LAs.  If you cannot
  resolve the issue, ask the instructor for clarification.
  \item Manage your time.  You have made a commitment to this course and
  will be expected to fulfill it.  Work and plan ahead.  Be aware of 
  upcoming due dates in this course as well as your own courses, research, 
  personal obligations, etc.  Plan ahead and make appropriate accommodations 
  if you know there will be an excess of work during a period of time.
\end{itemize}

\subsection*{Course Structure}

This course is structured with a single large lecture section with the
capacity to enroll nearly 300 students.  Despite the size, it is our 
goal to foster a greater sense of community among these students in 
our department and in our discipline.  

In addition to a traditional lecture, we've produced dozens of 
lecture/tutorial videos for students to view before and/or after lecture. 
The actual lectures will also be recorded and made available.
We also have extensive required reading (mostly from my free textbook but 
also supplemental resources).  

During the weekly labs, students will be randomly paired up and 
expected to complete several peer programming exercises.  They are 
expected to complete the labs in the lab time and are graded only on 
completion.

The course is structured such that each assignment is a phase in an
overall project.  The topic and specifics change from semester to 
semester, but each has the same basic structure of iteratively
building a full database-backed application.  Each phase is due on
Fridays at midnight.  Preceding each phase, students will submit a
design document draft that will be evaluated and returned to them
for improvements.  The design document serves several purposes including
giving students an early experience in technical writing, providing
an impetus for an early initial design phase, and to keep students 
on track and thinking about the project as a whole.

\subsection*{General Responsibilities}

\textbf{Learning Assistant} will have several responsibilities in 
addition to the responsibilities and expectations of the Learning 
Assistant program.

\begin{itemize}
  \item Assisting in 2-3 weekly lab and hack sessions
  \item Grading all materials (assignments and design document drafts)
  \item Mentoring and helping students in additional office hours, hack sessions
  and online via Piazza
  \item General administrative duties (entering grades, paperwork, etc.) as needed
  \item Other duties may include course development, materials development 
  (solution keys, future exercises, etc.) and other tasks identified by the instructor.
\end{itemize}

\textbf{Course Leaders} will have similar responsibilities as Learning
Assistants but may be asked to assume the responsibilities of other
Learning Assistants (such as assigned grading) in some cases.  Course
Leaders should also attend the weekly coordinating meetings and take
on a larger ``leadership'' role among the Learning Assistants.

Graduate Teaching Assistants will have the following general responsibilities
\begin{itemize}
  \item Supervising lab/hack sessions and assisting students in them
  \item Supervise grading and ensure that all assignments are graded 
    in a timely manner, shifting of responsibilities when issues arise, and ensuring quality and consistency in grading
  \item Holding regular office hours (at least 2 per week) within the
  designated area for the course
  \item Be in regular communication and hold weekly coordinating meetings with the instructor
\end{itemize}


\section*{Communication}

\begin{itemize}
  \item Piazza is our primary means of communication, use it and encourage 
students to use it.  
  \item If you receive email or canvas notifications from students, answer them 
but redirect them in the future to Piazza.  If the question/answer
would be of benefit to the class as a whole, post the question/answer
to Piazza and inform the student they can find the answer there.
  \item For communications among instructor(s), GTAs and LAs, use Piazza but
make it a private message, viewable only to TAs/instructors or the
individual(s) that it is intended for.
  \item If a question has been asked/answered before, link to the original
  post as your answer.
  \item Be professional in all your communications, be courteous and
  helpful.  
  \item Be prompt in answering communications.  No question or email should go 
  unanswered for more than 24 business hours.\footnote{Within 24 hours but only
  on business days, i.e.\ excluding weekends and holidays}
\end{itemize}

\section*{Grading}

\subsection*{Timeline}

\begin{itemize}
  \item Assignments are due on Fridays at midnight.  
  Randomized grading assignments will be sent out prior to the due 
  date/time.
  
  \item Design document drafts are due (hardcopy) in class on 
    Thursdays 1 week prior to the due date of the phase.  
    
  \item Learning Assistants are required to have completed their assigned
    grading by 5PM the following Tuesday (or within 48 business hours of
    the due date).  Upon completion Learning
    Assistants should be available via piazza and/or email for any 
    issues that need to be resolved.
  \item Graduate Teaching Assistants should have everything reviewed and
    any issues resolved by 5PM the following Thursday at which time 
    grades will be released to students.
  \item If Learning Assistants face any impediments or issues to completing
    their grading on time, they should discuss this with the instructor
    team as soon as possible.  Course Leaders or GTAs may be 
    responsible for helping to resolve the issue by either 
    temporarily helping with grading or shifting grading assignments.  
\end{itemize}

\subsection*{Directives}

\begin{itemize}
  \item All assignment grading is done through the online webgrader system.  
  \item Time is limited and it should not be wasted trying to troubleshoot 
    code that won't compile or run.  If the code is ungradeable or does not
    compile/run then take at most 5 minutes to look over
    the code.  If the issue can be fixed within that time frame, back up the
    original, fix it, note the differences (via code comments) and grade 
    accordingly.  If you cannot resolve the issue within 5 minutes, assign
    the student a zero and move on.  This will require you to login to the
    command line and edit the files directly.  Note that the original copy
    stored in the webhandin system will remain.
  \item Grade in accordance to the rubric through Canvas.  If the rubric 
    does not address something or there is a \emph{reasonable} uncertainty, 
    discuss it with the instruction team.
  \item Grade in a consistent manner, both between individual assignments and
    with other graders.  There should not be a significant variation in
    points deducted or awarded for similar mistakes or work.  Consistency 
    and grading quality will be checked by your GTA supervisor.
  \item When you deduct points, give clear and reasonably detailed reasons
    and justifications for doing so.  Good feedback is essential for the
    students' learning experience.  Put in efforts to provide constructive
    feedback and positive feedback for good work.
  \item By default the online rubric in canvas does not indicate to the
    student who graded the assignment.  To help the students, you are 
    \emph{required} to include a final comment on the assignment so 
    that the student can easily identify you.  Be positive and encouraging
    regardless of how well the student did.  You may also add comments to
    make any notes on changes or other administrative items (corrections, 
    regrades, etc.).
  \item In general, unless otherwise stated, the formatting of output is
    left up to the student.  As long as output formatting is reasonable and
    conveys \emph{just as much} information as the expected output, it should
    be graded as correct.
\end{itemize}



\end{document}
